My title

### 2024-11-01 paper/paper.qmd
abstract and intro part in paper updated citation mistake fixed

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Chenming Zhao
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder).
        We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis. The data is available at: [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{paper/tabularray}
pdf-engine: lualatex
---

@@

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

@@

# Model
Our model applies a hierarchical Bayesian approach, based on the framework proposed by @gelman2020regression. This method builds a layered structure that combines polling data collected by different organizations using various methodologies with regional and temporal trends to more accurately predict support rates on Election Day. Running within a Bayesian framework, our model employs a random walk prior to reflect the dynamically changing support rates following Biden's withdrawal in 2024. This prior distribution is based on historical election trends and the latest polling data, allowing the model to continuously update as new data becomes available.

@@

# Discussion

## Winner Prediction {#sec-pred}
Based on the support rate predictions for Trump at both the national and state levels displayed in @fig-results in @sec-results, it appears challenging for Trump to emerge victorious in the upcoming U.S. presidential election on November 5, 2024, against his primary opponent, Harris. The first chart shows the national support rate prediction for Trump, centering around 45% to 50%. Historically, any candidate needs to reach or exceed the 50% threshold to secure a decisive victory. The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with some possibility of winning.

@@

## Weaknesses and next steps {#sec-weakness}
In discussing the limitations of polls and our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior. Each step, from data collection to model construction, involves certain assumptions and potential biases. Below is a detailed discussion of these aspects:

### Defects of Existing Data {#sec-first-point}
Firstly, a major challenge for the model lies in estimating a large number of parameters with limited polling data. This scarcity of data can make the model highly sensitive to choices in priors and interstate covariance structures. For example, relying on historical patterns from states with limited data may fail to reflect the latest shifts in voter sentiment. This issue is also seen across different polling organizations and survey methods. As @gelman2020regression noted, the model can fluctuate between overconfidence and unreasonable uncertainty. To address this, we could consider incorporating alternative data sources, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas. However, these sources carry their own issues, as they may lack reliability and rigor.

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Chenming Zhao
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder).
        We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis. The data is available at: [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/)."
date: today
date-format: long
abstract: "This study aims to use a hierarchical Bayesian model to predict whether Donald Trump will win the 2024 U.S. presidential election based on support rates. By analyzing data of 2024 US presidential general election polls across states, pollsters, and methodologies, we capture variations in support for Trump driven by these factors. Our results reveal significant differences in support between national and state-level polls, with fluctuations in key swing states potentially influencing the election outcome. There is a dynamic interaction between election results and public opinion trends, and this study provides insights into how various factors influence public sentiment, offering valuable predictions and understanding of voter dynamics in the U.S. election."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{paper/tabularray}
pdf-engine: lualatex
---

@@

The U.S. presidential election has consistently captured the attention of nearly everyone. The 2024 U.S. presidential election is taking place against a backdrop of intense political polarization and complex shifts in public opinion. With changes in the social and economic landscape post-pandemic, the rise of differing ideologies, and frequent political controversies, forecasting the outcome of the 2024 election has become more challenging than ever. Statistics show that the U.S. presidential election is one of the world’s most expensive elections, involving massive amounts of money and manpower, and the 2024 election is expected to cost a record-breaking $15.9 billion (New York Times). Both the Democratic and Republican parties have poured significant resources and funds into the campaign, employing different strategies to win over voters (Reuters). The policy stances of different parties directly affect voters and national policies, and these differences will continue to influence the future direction of the electorate, the United States, and even the world. As the world’s largest economy, the U.S. policy shifts directly impact global markets. Changes in U.S. trade policy often lead to shifts in international trade dynamics, affecting the economic development of other countries. Additionally, the U.S. foreign policy and military strategy hold a dominant position in global affairs. The diplomatic stance of the new president may also alter relations with other countries, impacting global security.

In this paper, we focus on the outcome of the 2024 presidential election. Using a dataset from FiveThirtyEight containing extensive polling results, we examine the influence of various factors on candidate support rates by accounting for differences in polling methods, state-level variation, and temporal changes. It is evident that polling methods often fail to fully capture the complexity of public opinion, and factors that introduce bias may intervene from the very design of polling methods. The chaos and complexity of the real world are also reflected in a large-scale political event like the 2024 presidential election, which involves a vast number of participants, wide-ranging groups, and massive investments and interests. Therefore, we employ a hierarchical Bayesian model as a predictive tool in our analysis. This model integrates polling data from FiveThirtyEight covering various states and polling organizations, while also considering the effects of regional and methodological influences. By incorporating variables such as days since Biden’s withdrawal, polling methodology, and whether the poll is national or state-level, the model provides a dynamic view of Trump’s support rate across time and place. With an R² of 0.641 and an RMSE of 2.31, the model effectively captures these patterns while maintaining predictive accuracy, indicating that it can provide meaningful insights into regional and national public opinion trends. Finally, we simulate data for Election Day on November 5 to provide a reliable basis for predicting the election outcome.

Our analysis reveals that differences in Trump’s support rate across regions and polling methods are particularly pronounced. For example, support rates in traditionally conservative states like Texas differ significantly from those in traditionally liberal states like California, while trends in swing states such as Pennsylvania and Michigan are more unstable, with the potential to disrupt the election balance. This underscores the critical impact of geographic and methodological factors on public opinion, aligning well with the historical tendency of swing states to determine the election outcome. Additionally, our results suggest that polling methodologies introduce systematic differences in support rate estimation, with slight variations between results from online panels and phone surveys. In the predictive results, support for Trump at both the state and national levels hovers around 45% to 50%. Comparing this to the support rates of past U.S. presidents, we predict that Trump is unlikely to win in this election.

The remainder of this paper is structured as follows. @sec-data introduces the data sources, preprocessing steps, variable selection criteria, and the potential relationships between independent and dependent variables. @sec-model provides a concise explanation of the hierarchical Bayesian model, including the design rationale and selection of priors and random effects, with more details on the model’s posterior in [Appendix -@sec-model-details]. @sec-results presents the main findings of the study, including a summary of the model output to support its accuracy and predictions of Trump’s support rate across different regions on November 5, 2024. @sec-first in @sec-discussion discusses the implications of the results, @sec-second talks about limitations of the data and polls, complexity of conducting our real world into datas, and future directions.

@@

# Model {#sec-model}
Our model applies a hierarchical Bayesian approach, based on the framework proposed by @gelman2020regression. This method builds a layered structure that combines polling data collected by different organizations using various methodologies with regional and temporal trends to more accurately predict support rates on Election Day. Running within a Bayesian framework, our model employs a random walk prior to reflect the dynamically changing support rates following Biden's withdrawal in 2024. This prior distribution is based on historical election trends and the latest polling data, allowing the model to continuously update as new data becomes available.

@@

# Discussion {#sec-discussion}

## Winner Prediction {#sec-first}
Based on the support rate predictions for Trump at both the national and state levels displayed in @fig-results in @sec-results, it appears challenging for Trump to emerge victorious in the upcoming U.S. presidential election on November 5, 2024, against his primary opponent, Harris. The first chart shows the national support rate prediction for Trump, centering around 45% to 50%. Historically, any candidate needs to reach or exceed the 50% threshold to secure a decisive victory. The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with some possibility of winning.

@@

## Weaknesses and next steps {#sec-second}
In discussing the limitations of polls and our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior. Each step, from data collection to model construction, involves certain assumptions and potential biases. Below is a detailed discussion of these aspects:

### Defects of Existing Data
Firstly, a major challenge for the model lies in estimating a large number of parameters with limited polling data. This scarcity of data can make the model highly sensitive to choices in priors and interstate covariance structures. For example, relying on historical patterns from states with limited data may fail to reflect the latest shifts in voter sentiment. This issue is also seen across different polling organizations and survey methods. As @gelman2020regression noted, the model can fluctuate between overconfidence and unreasonable uncertainty. To address this, we could consider incorporating alternative data sources, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas. However, these sources carry their own issues, as they may lack reliability and rigor.
